%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\PassOptionsToPackage{
	colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,}{hyperref}
\documentclass[10 pt,a4paper,sans,unicode]{moderncv} 
% Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} 
% CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red} 
% CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'


\usepackage[scale=0.85]{geometry} 
% Reduce document margins
\setlength{\hintscolumnwidth}{1.85cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{25cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\firstname{Abdurrahman} % Your first name
\familyname{Idris} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Junior Android Developer}
\address{Elshahid Walid Elais street}{Alexandria, Egypt}
\mobile{(+20)1207249786}
%\mobile{(+2) 01552331245}
\email{eng.abdurrahman.idris@gmail.com}
\extrainfo{\href{https://github.com/AbdurrahmanIdris}{\githubsocialsymbol}~%
           \href{https://www.linkedin.com/in/abdurrahmanidris}{\linkedinsocialsymbol}~%
           abdurrahmanidris}
%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\cventry{2016--Present}{Bachelor's Degree}{}{}{\textit{Department of Electronics and Communications. \newline \link[Faculty of Engineering, Alexandria University]{https://eng.alexu.edu.eg/index.php/en/}}}{}


%----------------------------------------------------------------------------------------
%	Experinece SECTION
%----------------------------------------------------------------------------------------
\section{Experience}

\cvitem{July 2019 -\newline Present}{\textbf{Computer vision Engineer, Software team | \link[Croco Marine ROV team]{https://www.facebook.com/CrocoMarine/}}\newline
{I'm responsible for building solutions for \textbf{computer vision} and \textbf{machine learning} problems which helps the ROV to do autonomous tasks like detecting shapes and make decisions based on its detection.}}


%----------------------------------------------------------------------------------------
%	Professional Training SECTION
%----------------------------------------------------------------------------------------
\section{Professional training}
\cvitem{April 2020-\newline Present}{
\textbf{Google Africa Developer Scholarship | Android Development Track}\newline
\textit{by \link[PluralSight.com (My profile link)]{https://app.pluralsight.com/profile/abdurrahman-idris-bb} and \link[Andela.com]{https://andela.com/}}\newline
\begin{itemize}
\item I entered the \textbf{Registeration phase} and passed it with \textbf{\textit{+11 watching hours}} and accepted to join \textbf{Phase 1} of the program. 
\item My goal in this program is to become a Certified Android Developer from Google.
\end{itemize}}
\cvitem{April 2020}{
\textbf{Android applications programming}, by \link[Edraak.org]{www.edraak.org} \link[\textbf{\textit{(Course Certificate)}}]{https://drive.google.com/file/d/1MI46T_i5us3-l_qAA5AgovFn0o5anz_S/view}
\newline
{
\begin{itemize}
\item I mastered the basics of Java. This includes implementations, interfaces, and algorithms. It also helped me to understand and write data-bases, as well as operate comfortably with object-oriented programming. I also learned to handle exceptions and perform debugging procedures on existing code. \link[\textbf{\textit{Github}}] {https://github.com/AbdurrahmanIdris/Android-Development-Course-by-Edraak.git}
\item  I learned beginning Android programming concepts using the Java programming language, and built a variety of basic apps using Android Studio. \link[\textbf{\textit{Github}}] {https://github.com/AbdurrahmanIdris/Android-Apps.git}
\end{itemize}
}
}
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Honor and Award}

\cvitem{March 2020}{
{\textbf{Gold Medal and Top 50 in Huawei ICT Competition National Exam}}
\newline
{
\begin{itemize}
\item After about 5 months of hard working. I achieved my goal and get the gold medal plus a good knowledge and experience about \textbf{Cloud Computing} field.
\end{itemize}
}}

%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}
%
\cvitem{Industry Knowledge}{\textsc{\textbf{Android Development}, Computer Vision,  Data Visualization, Machine Learning, Data Science}}
\cvitem{Languages}{\textsc{\textbf{Java}, \textbf{XML}, Python, C, SQL, Matlab, HTML, CSS}}

%----------------------------------------------------------------------------------------
%	Volunteering SECTION
%----------------------------------------------------------------------------------------
\section{Volunteering}
\cvitem{Oct 19-Now}{
{\textbf{Translator} | \textbf{Coursera.org}}
{English to Arabic translator. Translated +1000 words in different courses.}
}
\cvitem{Dec19-Now}{
{\textbf{Media and Marketing Committee member} | \textbf{Student Union F.O.E Alexandria University }}
}
%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
\section{Languages}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Arabic}{Native}{}

\end{document}



